Optimizing a PoS Tag Set for Dependency Parsing

### 2016-05-03 submission.tex
Additions to previous work by MacKinlay and Megyesi

\section{Previous/Related work}
\label{sec:prev}
There is a considerable lack of previous efforts on extrinsic evaluation of the
effects of PoS tag sets on downstream applications. We will consider(/noe
annet, considerable...consider) papers that evaluate the effects of PoS tag
set granularity on PoS tagging. This includes investigation of the effects of
PoS tag sets on tagging of Swedish \cite{Meg:01,Meg:02} and English
\cite{Mac:05}. Increases in tagger accuracy does not readily translate to
improved parsing.

@@

Similarly, \newcite{Mac:05} investigated the effects of PoS tag sets on PoS
tagger performance in English, specifically the Penn Treebank
\cite{Mar:San:Mar:93}. They mapped the original tag set of Penn Treebank to
more fine-grained tag sets "in terms of" linguistic utility. the additional
linguistic information included in the tags may assist the tagger.
utility/motivation to investigate whether linguistically motivated tag set
modifications can improve the tagger accuracy while increasing the linguistic
information in the tag set. Experimenting with both morphologically and
syntactically motivated modifications, they found that more fine-grained
tag sets rarely led to improvements in tagger accuracy,
where the most successful modification yielded an improvement in tagger
accuracy of 0.05 percentage points.

@@

\begin{table}
    \centering
    \smaller[0.5]
    \begin{tabular}{@{}ll@{}}
        \toprule
        \textbf{Tag} & \textbf{Description} \\
        \midrule
        \texttt{adj} & Adjective \\
        \texttt{adv} & Adverb \\
        \texttt{det} & Determiner\\
        \texttt{inf-merke} & Infinitive marker \\
        \texttt{interj} & Interjection \\
        \texttt{konj} & Conjunction \\
        \texttt{prep} & Preposition \\
        \texttt{pron} & Pronoun \\
        \texttt{sbu} & Subordinate conjunction \\
        \texttt{subst} & Noun \\
        \texttt{ukjent} & Unknown (foreign word) \\
        \texttt{verb} & Verb \\
        \bottomrule
    \end{tabular}
    \caption{Overview of the tag set of NDT.}
    \label{ndttagest}
\end{table}

>>>>

\section{Previous/Related work}
\label{sec:prev}
There is a considerable lack of previous efforts on extrinsic evaluation of the
effects of PoS tag sets on downstream applications. We will consider(/noe
annet, considerable...consider) papers that evaluate the effects of PoS tag
set granularity on PoS tagging. This includes investigation of the effects of
PoS tag sets on tagging of Swedish \cite{Meg:01,Meg:02} and English
\cite{Mac:05}.

%Increases in tagger accuracy does not readily translate to
%improved parsing.

@@

Similarly, \newcite{Mac:05} investigated the effects of PoS tag sets on tagger
performance in English, specifically the Wall Street Journal portion of Penn
Treebank \cite{Mar:San:Mar:93}. They mapped the original tag set of Penn
Treebank to more fine-grained tag sets using linguistic insight to investigate
whether the additional linguistic information included in the finer-grained
tags could assist the tagger. Experimenting with both lexically and
syntactically conditioned modifications such as distinguishing between count
nouns and noncount nouns as well as between transitive and intransitive verbs,
they found that more fine-grained tag sets rarely led to improvements in tagger
accuracy; the most successful modification yielded an improvement in tagger
accuracy of 0.05 percentage points.

Transition/overgang her ...

@@

\begin{table}
    \centering
    %\smaller[0.5]
    \begin{tabular}{@{}ll@{}}
        \toprule
        \textbf{Tag} & \textbf{Description} \\
        \midrule
        \texttt{adj} & Adjective \\
        \texttt{adv} & Adverb \\
        \texttt{det} & Determiner\\
        \texttt{inf-merke} & Infinitive marker \\
        \texttt{interj} & Interjection \\
        \texttt{konj} & Conjunction \\
        \texttt{prep} & Preposition \\
        \texttt{pron} & Pronoun \\
        \texttt{sbu} & Subordinate conjunction \\
        \texttt{subst} & Noun \\
        \texttt{ukjent} & Unknown (foreign word) \\
        \texttt{verb} & Verb \\
        \bottomrule
    \end{tabular}
    \caption{Overview of the PoS tag set of NDT.}
    \label{ndttagest}
\end{table}
